Analytical reproducibility and data reusability of published meta-analyses on clinical psychological

### 2022-11-25 manuscript.Rmd
Minor changues

---
title: "Analytical reproducibility and data reusability of published meta-analyses on clinical psychological
  interventions"
shorttitle: "Meta-analyses reproducibility"
leftheader: "Lopez-Nicolas et al."

@@

author_note: |
 All materials, data, and analysis script coded have been made publicly available on the Open Science Framework: https://osf.io/6cmzh/. This research has been funded with a grant from the Spanish Ministry of Science and Innovation by FEDER funds (Project nº PID2019-104080GB-I00), and by a predoctoral grant (FPU18/04805) from the Spanish Ministry of Universities.The funders had no role in study design, data collection and analysis, decision to publish, or preparation of the manuscript.

@@

class             : "jou, a4paper"
output            : papaja::apa6_pdf
header-includes:
   - \usepackage{caption}
   - \captionsetup[table]{textfont={it}, labelfont={bf}, singlelinecheck=false, labelsep=newline}
   - \captionsetup[figure]{textfont={it}, labelfont={bf}, singlelinecheck=false, labelsep=newline}
---

Meta-analysis is widely considered as an important approach to evaluate a body of work. Given the ongoing growth in the number of scientific publications [@bornmann2021], evidence synthesis approaches -such as meta-analysis- are becoming increasingly relevant for a cumulative science. This relevance rests on the credibility of meta-analytic results, which can be threatened by a lack of rigorous application or poor-quality reporting [@gurevitch2018]. Given the importance of meta-analyses for evidence-based practice, these threats to their credibility need to be closely monitored.
In recent years different concerns on credibility of  empirical claims have emerged. Several projects have systematically attempted to assess the replicability and reproducibility of published scientific results (e.g., @artner2020; @errington2021a; @opensciencecollaboration2015). Those initiatives showed many failures to replicate or reproduce the published results. In this context, the empirical assessment of scientific published results credibility has become a major task for the scientific community.

@@

Several reproducibility analyses of meta-analyses have been performed in recent years. For example, some process reproducibility assessments have shown an important lack of data availability in machine-readable formats, and an almost complete absence of analysis script code availability [@lopez-nicolas2021; @polanin2020]. Furthermore, some outcome reproducibility assessments have shown a considerable number of failures when trying to reproduce the primary effect sizes of some published meta-analyses by recollecting primary data from primary studies [@gotzsche2007; @maassen2020; @tendal2009] possibly due to lack of details on how primary effect sizes were selected and computed. In these outcome reproducibility studies, the main task entails reconstructing the original data by retrieving them from the source, namely the included primary studies. Thus, their assessment focus is on this stage of the analysis pipeline of a meta-analysis, which usually involves decisions on how to select the primary outcomes and how to deal with possible dependency, and the computation of (standardized) effect sizes. Figure 1 displays a summary of the basic meta-analysis pipeline through a flowchart, outlining the different stages and listing previous work that has explored different facets of reproducibility of these, as well as the required elements to be able to reproduce each stage.

@@

Reproducibility analysis typically uses the original data available from the original authors (e.g., [@artner2020; @hardwicke2021; @hardwicke2018]. This puts the focus of the assessment at factors such as the reusability of the available data, challenges for the reconstruction of the original analysis scheme, reporting errors, etc.   Although data availability seems to have improved in the last years [@hardwicke2018; @tedersoo2021; @wallach2018], systematic reviews and meta-analyses appear to be a special case. Typically, the data collected for a meta-analysis is study-level summary data extracted from published primary studies which is commonly reported in the paper through tables or forest plots. This may lead to the idea that common data sharing practices do not apply to meta-analysis. For example, @page2022 analysed the content of data availability statements from a set of meta-analyses published in 2020. Only 31% included a data availability statement and only 13% of these included a link to access the data openly, with 23% stating that all relevant data are available in the paper itself, 10% stating that data sharing is not applicable as no datasets were generated, 8% stating that data sharing is not applicable as the data is drawn from already published literature, and 42% stating that data were available upon request. It is surprising that, even just considering meta-analyses that included a data availability statement, the authors of these meta-analysis  assume that such practices do not apply to meta-analyses or that the data in the article itself is sufficient.

@@

# Method
## Preregistration
The pre-data analysis protocol (https://osf.io/42r3p/) was pre-registered on 19 October 2021. Any deviation from this protocol is explicitly acknowledged.

@@

## Retrieval of primary data
The availability of necessary primary data was checked. First, we searched for machine-readable data files through links leading to third-party repositories or in supplementary material hosted by the journal. Second, we looked for available data through tables or forest plots in the meta-analytic report itself, or in supplementary material. In these cases, the primary data had to be manually re-coded to reuse it. Finally, if the primary data of a meta-analysis were not directly available after the previous steps, we attempted to obtain the data through a request to the corresponding author identified in the associated paper. We sent an initial request in June 2021 and, if there was no reply, a subsequent reminder in October 2021. This reminder was sent to a more recent alternative email address if we were able to find one. If we were unable to obtain the data through the email request, the associated meta-analysis was labelled as not process reproducible.  
In order to be able to reproduce meta-analyses, primary effects and their associated standard errors are required. These are generally computed from primary statistics retrieved from the primary studies such as means, standard deviations or sample sizes. We attempted to retrieve the least processed data possible. First, we sought for the primary statistics, recovered in `r sprintf("%0.0f%%", df_type_of_data$perc[3] * 100)` of the cases. Second, we sought for the primary effects and their standard errors (or, alternatively, the sampling variances), recovered in `r sprintf("%0.0f%%", df_type_of_data$perc[2] * 100)` of the cases. Finally, we sought for the primary effects and their confidential limits, recovered in `r sprintf("%0.0f%%", df_type_of_data$perc[1] * 100)` of the cases, from which the standard errors were approximated as follows:

@@

## Reconstructing the original analytical scheme
To proceed with reproducibility attempts of the meta-analyses that were labelled as process reproducible, we first looked for the availability of the original analysis script. When it was available, analytical reproducibility was checked by rerunning the original script on the associated primary data. In `r df_process_rep$n[2] -  n_mas_w_script` cases (`r sprintf("%0.0f%%", 100-((n_mas_w_script/df_process_rep$n[2]) * 100))`), the analysis script code was not available. In these cases we tried to reconstruct the original analytical scheme using the technical details reported in the paper. Specifically, we collected information on: (a) the meta-analytic model originally assumed; (b) the weighting scheme; (c) the between-studies variance estimator; (d) the method used to compute the confidence interval; and (e) the software used to perform the meta-analysis. If any of these details about the analytical methods were not reported, but the software used was mentioned, we inferred the first four pieces of information from the default settings of the software used. If the software used was not reported, we inferred this information from the default settings of the most used software in the sample, which was *Comprehensive Meta-Analysis*. Additional information about the meta-analysis was collected that is not reported in this manuscript. The full list of variables collected is available in the Protocol (https://osf.io/tq4uf/) and a Codebook describing these variables is available at: https://osf.io/ym78s/.

@@

## Reproducibility outcomes
Each meta-analysis was labelled using the following reproducibility success scheme: (a) reproducible; (b) not process-reproducible; (c) numerical error, and (d) decision error. Not process-reproducible refers to situations where we were unable to access the primary data neither through direct extraction nor upon request. Similar to previous studies (Artner et al., 2020; Hardwicke et al., 2018, 2021) an index of numerical error was computed (see Protocol https://osf.io/tq4uf/). This index expressed the difference between reproduced and original values as a percentage. To avoid labelling minor numerical discrepancies related to numerical rounding as reproducibility problems, a 5% discrepancy threshold was set. Thus, a meta-analysis was labelled as 'numerical error' if it showed a discrepancy larger than 5%.^[A sensitivity analysis using other possible criteria is reported in the supplementary file.] 
Finally, the label 'decision error' refers to situations where the $p_{reported}$ fell on the opposite side of the .05 boundary in relation to the $p_{reproduced}$. 
We focus on analytical reproducibility of summary effects, their confidence bounds and the result of the null hypothesis significance test. Secondarily, we also assessed analytical reproducibility of other synthesis methods such as heterogeneity statistics.

@@

## Original authors clarifications
These `r nrow(df_to_rev2)` meta-analyses were from `r sum(df_success_request$n)` different papers. Therefore, `r sum(df_success_request$n)` clarification requests with information about the study aims, methods and preliminary results were sent to the corresponding authors of the original articles. A reply was received in only `r df_success_request$n[2]`  of the `r sum(df_success_request$n)` cases.
In one of them, the original authors sent back a link to an OSF repository where the original data and analysis script were stored. According to the authors, this link was not reported in the paper by mistake. The script was run on these data and the results were successfully reproduced. In this case, the data previously used were retrieved from a forest plot (means and standard deviations) and a table (sample sizes) reported in the paper. The previous discrepancy was explained by two cases included in the original meta-analysis from the same primary study that were reported with the same ID in the forest plot and were not correctly matched with their corresponding sample size extracted from the table. This situation exemplifies the potential issues arising from having to reconstruct the original data from tables and figures and not having open access to the original data file. 
In the other case, the original data was retrieved from a huge table in supplementary material with all effect sizes and their confidence limits. The original authors sent back this same table by increasing the number of decimal places of the effect sizes and after correcting some wrong values that they themselves detected in that process. This fixed the discrepancies for some of the meta-analyses in this paper.

@@

Even when we interpret data availability in the broad sense (i.e. retrieving data from tables and figures when no data file was available), for about a third of the included meta-analyses no data was available.  In these cases, attempts were made to obtain the data on request to the corresponding author, with little success.Authors only shared data in 12% of the requests that were made. This result is in line with what was found in a recent study where data availability statements from a set of primary studies were analysed [@gabelica2022].Where 42% of primary studies in @gabelica2022 reported data was available on request (and identical percentage was found in @page2022 for meta-analyses), only 6.8% of the authors shared the underlying data when requested. Even though it is common to see authors state data is available on request, actually obtaining the data on request seems highly challenging. Although this problem of retrieving data on request is well known [@wicherts2006], the situation does not seem to have improved. Nowadays, there are straightforward, free, and open ways to share data, including meta-analytic data files. Several repositories (e.g., OSF, GitHub, Zenodo, Figshare) are available for researchers to openly share the data associated with published results. On-request availability has proven to be inadequate, and with the availability of data repositories is no longer necessary. Journals publishing meta-analyses should require that authors share the underlying data in a public data repository.

For the remaining meta-analyses (about two thirds), we were able to retrieve the data used by the original authors. In only 5% of these cases data was shared in a machine-readable data file (e.g., *csv*, *xlsx*, ...), while the data had to be retrieved from files in document format (e.g., *docx*, *pdf*) for the rest of cases. This forces people who want to re-use the data to manually recode the data, which is both inefficient and error-prone task. Even after partial double coding was carried out, this procedure did not avoid some coding errors, which were detected by double checking meta-analyses with discrepancies. In out experience, the data retrieval process can be difficult when results are presented in general tables, as it involves matching subsets of these primary data with different meta-analytic results, while is not always clear which studies were used in which meta-analysis reported in a paper. Furthermore, because the tables in manuscript are often generated manually in document file formats (e.g. Word), we observed examples where this introduced another source of error. There are good guidelines on how to share research data properly [@wilkinson2016], and authors should share data in machine-readable formats.

@@

Despite these difficulties, we were able to recover the original data and reconstruct the original analysis approach, for 146 meta-analyses, for which the analytical reproducibility of the results was assessed. These attempts at analytical reproduction went through several stages as explained above, trying to minimize the impact of possible coding errors, and requesting clarifications from the original authors. Nevertheless, even with these efforts, some discrepancies remained in the results. We identified different issued that hindered our reproducibility attempts. For example, in some cases internal discrepancies were found in the paper itself (e.g., text-figure discrepancies, text-abstract, or text-table discrepancies). Furthermore, some problems were found with the lack of some primary data, where data available in the supplementary material included fewer cases than those finally reported in the results of the published paper. These situations could be explained by typos in the manuscript, or updates when performing the meta-analysis that produced different versions of the manuscript, data, or supplementary material. While it is important to note that discrepancies in the summary effect results and their confidence intervals were mostly minor, with little or no impact on the conclusions, these situations are easily avoidable. Some of the problems identified could be explained by typos. Currently, there are tools that facilitate the production of so-called reproducible manuscripts, such as the R packages *kintr* [@xie2022] and *rmarkdown* [@allaire2022]. A reproducible manuscript embeds analysis code, data and results reporting in a single document, extracting and reporting the results from the output of the computational process itself, avoiding error-prone manual transcriptions.

@@

## Funding 
This research has been funded with a grant from the Spanish Ministry of Science and Innovation (Project PID2019-104080GB-I00, FEDER funds) and by the Spanish Ministry of Universities (predoctoral grant: FPU18/04805).

@@

## Prior versions

>>>>

---
title: "Analytical reproducibility and data reusability of published meta-analyses on clinical psychological
  interventions"
shorttitle: "Meta-analyses reproducibility (PRE-PRINT)"
leftheader: "Lopez-Nicolas et al."

@@

@@

class             : "apa7"
output            : papaja::apa6_pdf
header-includes:
   - \usepackage{caption}
   - \captionsetup[table]{textfont={it}, labelfont={bf}, singlelinecheck=false, labelsep=newline}
   - \captionsetup[figure]{textfont={it}, labelfont={bf}, singlelinecheck=false, labelsep=newline}
---

Meta-analysis is widely considered as an important approach to evaluate a body of work. Given the ongoing growth in the number of scientific publications [@bornmann2021], evidence synthesis approaches -such as meta-analysis- are becoming increasingly relevant for a cumulative science. This relevance rests on the credibility of meta-analytic results, which can be threatened by a lack of rigorous application or poor-quality reporting [@gurevitch2018]. Given the importance of meta-analyses for evidence-based practice, these threats to their credibility need to be closely monitored.

In recent years different concerns on credibility of  empirical claims have emerged. Several projects have systematically attempted to assess the replicability and reproducibility of published scientific results (e.g., @artner2020; @errington2021a; @opensciencecollaboration2015). Those initiatives showed many failures to replicate or reproduce the published results. In this context, the empirical assessment of scientific published results credibility has become a major task for the scientific community.

@@

Several reproducibility analyses of meta-analyses have been performed in recent years. For example, some process reproducibility assessments have shown an important lack of data availability in machine-readable formats, and an almost complete absence of analysis script code availability [@lopez-nicolas2021; @polanin2020]. Furthermore, some outcome reproducibility assessments have shown a considerable number of failures when trying to reproduce the primary effect sizes of some published meta-analyses by recollecting primary data from primary studies [@gotzsche2007; @maassen2020; @tendal2009] possibly due to lack of details on how primary effect sizes were selected and computed. In these outcome reproducibility studies, the main task entails reconstructing the original data by retrieving them from the source, namely the included primary studies. Thus, their assessment focus is on this stage of the analysis pipeline of a meta-analysis, which usually involves decisions on how to select the primary outcomes and how to deal with possible dependency, and the computation of (standardized) effect sizes. Figure 1 displays a summary of the basic meta-analysis pipeline through a flowchart, outlining the different stages and listing previous work that has explored different facets of reproducibility of these, as well as a summary of the required elements to be able to reproduce each stage.

@@

Reproducibility analysis typically uses the original data available from the original authors [e.g., @artner2020; @hardwicke2021; @hardwicke2018]. This puts the focus of the assessment at factors such as the reusability of the available data, challenges for the reconstruction of the original analysis scheme, reporting errors, etc.   Although data availability seems to have improved in the last years [@hardwicke2018; @tedersoo2021; @wallach2018], systematic reviews and meta-analyses appear to be a special case. Typically, the data collected for a meta-analysis is study-level summary data extracted from published primary studies which is commonly reported in the paper through tables or forest plots. This may lead to the idea that common data sharing practices do not apply to meta-analysis. For example, @page2022 analysed the content of data availability statements from a set of meta-analyses published in 2020. Only 31% included a data availability statement and only 13% of these included a link to access the data openly, with 23% stating that all relevant data are available in the paper itself, 10% stating that data sharing is not applicable as no datasets were generated, 8% stating that data sharing is not applicable as the data is drawn from already published literature, and 42% stating that data were available upon request. It is surprising that, even just considering meta-analyses that included a data availability statement, the authors of these meta-analysis  assume that such practices do not apply to meta-analyses or that the data in the article itself is sufficient.

@@

# Method
## Preregistration
The pre-data analysis protocol (https://doi.org/10.17605/OSF.IO/79J2T) was pre-registered on 19 October 2021. Any deviation from this protocol is explicitly acknowledged.

@@

## Retrieval of primary data
The availability of necessary primary data was checked. First, we searched for machine-readable data files through links leading to third-party repositories or in supplementary material hosted by the journal. Second, we looked for available data through tables or forest plots in the meta-analytic report itself, or in supplementary material. In these cases, the primary data had to be manually re-coded to reuse it. Finally, if the primary data of a meta-analysis were not directly available after the previous steps, we attempted to obtain the data through a request to the corresponding author identified in the associated paper. We sent an initial request in June 2021 and, if there was no reply, a subsequent reminder in October 2021. This reminder was sent to a more recent alternative email address if we were able to find one. If we were unable to obtain the data through the email request, the associated meta-analysis was labelled as not process reproducible.

In order to be able to reproduce meta-analyses, primary effects and their associated standard errors are required. These are generally computed from primary statistics retrieved from the primary studies such as means, standard deviations or sample sizes. We attempted to retrieve the least processed data possible. First, we sought for the primary statistics, recovered in `r sprintf("%0.0f%%", df_type_of_data$perc[3] * 100)` of the cases. Second, we sought for the primary effects and their standard errors (or, alternatively, the sampling variances), recovered in `r sprintf("%0.0f%%", df_type_of_data$perc[2] * 100)` of the cases. Finally, we sought for the primary effects and their confidential limits, recovered in `r sprintf("%0.0f%%", df_type_of_data$perc[1] * 100)` of the cases, from which the standard errors were approximated as follows:

@@

## Reconstructing the original analytical scheme
To proceed with reproducibility attempts of the meta-analyses that were labelled as process reproducible, we first looked for the availability of the original analysis script. When it was available, analytical reproducibility was checked by rerunning the original script on the associated primary data. In `r df_process_rep$n[2] -  n_mas_w_script` cases (`r sprintf("%0.0f%%", 100-((n_mas_w_script/df_process_rep$n[2]) * 100))`), the analysis script code was not available. In these cases we tried to reconstruct the original analytical scheme using the technical details reported in the paper. Specifically, we collected information on: (a) the meta-analytic model originally assumed; (b) the weighting scheme; (c) the between-studies variance estimator; (d) the method used to compute the confidence interval; and (e) the software used to perform the meta-analysis. If any of these details about the analytical methods were not reported, but the software used was mentioned, we inferred the first four pieces of information from the default settings of the software used. If the software used was not reported, we inferred this information from the default settings of the most used software in the sample, which was *Comprehensive Meta-Analysis*.

Additional information about the meta-analysis was collected that is not reported in this manuscript. The full list of variables collected is available in the Protocol (https://osf.io/tq4uf/) and a Codebook describing these variables is available at: https://osf.io/ym78s/.

@@

## Reproducibility outcomes
Each meta-analysis was labelled using the following reproducibility success scheme: (a) reproducible; (b) not process-reproducible; (c) numerical error, and (d) decision error. Not process-reproducible refers to situations where we were unable to access the primary data neither through direct extraction nor upon request. Similar to previous studies (Artner et al., 2020; Hardwicke et al., 2018, 2021) an index of numerical error was computed (see Protocol https://osf.io/tq4uf/). This index expressed the difference between reproduced and original values as a percentage. To avoid labelling minor numerical discrepancies related to numerical rounding as reproducibility problems, a 5% discrepancy threshold was set. Thus, a meta-analysis was labelled as 'numerical error' if it showed a discrepancy larger than 5%.^[A sensitivity analysis using other possible criteria is reported in the supplementary file.] 
Finally, the label 'decision error' refers to situations where the $p_{reported}$ fell on the opposite side of the .05 boundary in relation to the $p_{reproduced}$.

We focus on analytical reproducibility of summary effects, their confidence bounds and the result of the null hypothesis significance test. Secondarily, we also assessed analytical reproducibility of other synthesis methods such as heterogeneity statistics.

@@

## Original authors clarifications
These `r nrow(df_to_rev2)` meta-analyses were from `r sum(df_success_request$n)` different papers. Therefore, `r sum(df_success_request$n)` clarification requests with information about the study aims, methods and preliminary results were sent to the corresponding authors of the original articles. A reply was received in only `r df_success_request$n[2]`  of the `r sum(df_success_request$n)` cases.
In one of them, the original authors sent back a link to an OSF repository where the original data and analysis script were stored. According to the authors, this link was not reported in the paper by mistake. The script was run on these data and the results were successfully reproduced. In this case, the data previously used were retrieved from a forest plot (means and standard deviations) and a table (sample sizes) reported in the paper. The previous discrepancy was explained by two cases included in the original meta-analysis from the same primary study that were reported with the same ID in the forest plot and were not correctly matched with their corresponding sample size extracted from the table. This situation exemplifies the potential issues arising from having to reconstruct the original data from tables and figures and not having open access to the original data file.

In the other case, the original data was retrieved from a huge table in supplementary material with all effect sizes and their confidence limits. The original authors sent back this same table by increasing the number of decimal places of the effect sizes and after correcting some wrong values that they themselves detected in that process. This fixed the discrepancies for some of the meta-analyses in this paper.

@@

Even when we interpret data availability in the broad sense (i.e. retrieving data from tables and figures when no data file was available), for about a third of the included meta-analyses no data was available.  In these cases, attempts were made to obtain the data on request to the corresponding author, with little success. Authors only shared data in 12% of the requests that were made. This result is in line with what was found in a recent study where data availability statements from a set of primary studies were analysed [@gabelica2022].Where 42% of primary studies in @gabelica2022 reported data was available on request (and identical percentage was found in @page2022 for meta-analyses), only 6.8% of the authors shared the underlying data when requested. Even though it is common to see authors state data is available on request, actually obtaining the data on request seems highly challenging. Although this problem of retrieving data on request is well known [@wicherts2006], the situation does not seem to have improved. Nowadays, there are straightforward, free, and open ways to share data, including meta-analytic data files. Several repositories (e.g., OSF, GitHub, Zenodo, Figshare) are available for researchers to openly share the data associated with published results. On-request availability has proven to be inadequate, and with the availability of data repositories is no longer necessary. Journals publishing meta-analyses should require that authors share the underlying data in a public data repository.

For the remaining meta-analyses (about two thirds), we were able to retrieve the data used by the original authors. In only 5% of these cases data was shared in a machine-readable data file (e.g., *csv*, *xlsx*), while the data had to be retrieved from files in document format (e.g., *docx*, *pdf*) for the rest of cases. This forces people who want to re-use the data to manually recode the data, which is both inefficient and error-prone task. Even after partial double coding was carried out, this procedure did not avoid some coding errors, which were detected by double checking meta-analyses with discrepancies. In out experience, the data retrieval process can be difficult when results are presented in general tables, as it involves matching subsets of these primary data with different meta-analytic results, while is not always clear which studies were used in which meta-analysis reported in a paper. Furthermore, because the tables in manuscript are often generated manually in document file formats (e.g. Word), we observed examples where this introduced another source of error. There are good guidelines on how to share research data properly [@wilkinson2016], and authors should share data in machine-readable formats.

@@

Despite these difficulties, we were able to recover the original data and reconstruct the original analysis approach, for 146 meta-analyses, for which the analytical reproducibility of the results was assessed. These attempts at analytical reproduction went through several stages as explained above, trying to minimize the impact of possible coding errors, and requesting clarifications from the original authors. Nevertheless, even with these efforts, some discrepancies remained in the results. We identified different issued that hindered our reproducibility attempts. For example, in some cases internal discrepancies were found in the paper itself (e.g., text-figure discrepancies, text-abstract, or text-table discrepancies). Furthermore, some problems were found with the lack of some primary data, where data available in the supplementary material included fewer cases than those finally reported in the results of the published paper. These situations could be explained by typos in the manuscript, or updates when performing the meta-analysis that produced different versions of the manuscript, data, or supplementary material. While it is important to note that discrepancies in the summary effect results and their confidence intervals were mostly minor, with little or no impact on the conclusions, these situations are easily avoidable. Some of the problems identified could be explained by typos. Currently, there are tools that facilitate the production of so-called reproducible manuscripts, such as the R packages *kintr* [@xie2022], *rmarkdown* [@allaire2022], and *papaja* [@aust2022]. A reproducible manuscript embeds analysis code, data and results reporting in a single document, extracting and reporting the results from the output of the computational process itself, avoiding error-prone manual transcriptions.

@@

## Funding 
This research has been funded with a grant from the Spanish Ministry of Science and Innovation (Project PID2019-104080GB-I00/AEI/10.13039/501100011033, FEDER funds) and by the Spanish Ministry of Universities (predoctoral grant: FPU18/04805).

@@

Supplementary material available at: https://osf.io/fjhpw
